---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# SKBD

<!-- badges: start -->
[![R-CMD-check](https://github.com/Jiangyan-Zhao/SKBD/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Jiangyan-Zhao/SKBD/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`SKBD` implements the **Shared Keyboard Design (SKBD)** for model-assisted phase I dose-finding trials.

It provides practical tools for:

- generating SKBD decision tables,
- evaluating trial operating characteristics through simulation,
- extending SKBD to time-to-event settings with delayed toxicity outcomes, and
- assessing adaptive dose insertion under a shared-borrowing framework.

The package is designed for method development, simulation-based validation, and practical trial-planning workflows in early oncology studies.

## Installation

`SKBD` is not currently on CRAN. Install the development version from GitHub:

```{r install, eval = FALSE}
install.packages("remotes")
remotes::install_github("Jiangyan-Zhao/SKBD")
```

Then load the package:

```{r load}
library(SKBD)
```

## Main functions

The current public interface includes five core functions:

- `get_boundary_SKBD()` generates pre-tabulated decision boundaries for the shared keyboard design.
- `get_OC_SKBD()` simulates operating characteristics for the standard SKBD.
- `get_OC_TITE_SKBD()` simulates operating characteristics for time-to-event SKBD.
- `get_OC_Insert_SKBD()` simulates operating characteristics when adaptive dose insertion is enabled.
- `PUA()` generates monotone dose-toxicity scenarios using a pseudo-uniform algorithm.

## Shiny app (interactive interface)

A Shiny app is included for interactive use of SKBD decision tables and simulation outputs.

### What you can do in the app

- Configure trial design settings (dose levels, target toxicity, borrowing strength, sample size, and overdose control).
- Input current trial observations and generate SKBD decision tables in one click.
- Run multi-scenario operating-characteristic simulations from either manual entry or uploaded CSV templates.

### Launch the app

After installing the package, run:

```r
shiny::runApp(system.file("app", package = "SKBD"))
```

The app includes two tabs:

- **Trial Setting**: interactive boundary table generation.
- **Simulation**: batch scenario simulation and summary reporting.

## Decision tables for SKBD

A typical starting point is to generate a decision table at the current dose level, conditional on observed data across doses.

```{r boundary-example}
y <- c(0, 1, 2, 2, 0)
n <- c(3, 6, 9, 3, 0)

out_boundary <- get_boundary_SKBD(
  target_prob = 0.30,
  d = 3,
  y = y,
  n = n,
  table_type = "continue"
)

out_boundary$boundary_tab
```

This returns a keyboard-style table with escalation, de-escalation, and elimination boundaries based on the SKBD pseudo-posterior at the current dose.

## Simulating operating characteristics under SKBD

Evaluate the standard SKBD under a prespecified toxicity scenario:

```{r oc-skbd}
out_skbd <- get_OC_SKBD(
  target_prob = 0.30,
  tox_prob = c(0.05, 0.12, 0.30, 0.45, 0.60),
  n_cohort = 10,
  cohort_size = 3,
  n_trial = 1000
)

out_skbd$PCS
out_skbd$PCA
out_skbd$ROD60
```

The returned object includes safety and accuracy summaries such as percent correct selection (`PCS`), percent correct allocation (`PCA`), and overdosing risk.

## Time-to-event SKBD

Delayed toxicity can be handled using time-to-event SKBD:

```{r oc-tite}
out_tite <- get_OC_TITE_SKBD(
  target_prob = 0.20,
  tox_prob = c(0.05, 0.12, 0.20, 0.35, 0.50),
  n_cohort = 10,
  cohort_size = 3,
  tau = 3,
  accrual = 2,
  dist_DLT = "weibull",
  dist_enter = "exp",
  n_trial = 1000
)

out_tite$PCS
out_tite$duration_mean
```

This version accounts for pending toxicity outcomes through weighted follow-up in the DLT assessment window.

## Adaptive dose insertion

The package also supports simulations under insertion-enabled shared keyboard designs:

```{r oc-insert, eval = FALSE}
out_insert <- get_OC_Insert_SKBD(
  target_prob = 0.30,
  tox_prob = c(0.14, 0.45, 0.63, 0.74, 0.80),
  dose_set = c(5, 15, 25, 35, 45),
  n_trial = 1000
)

out_insert$insertion
```

The insertion summary reports how often new doses are added, where inserted doses tend to be selected, and how patients are allocated to inserted doses.

## Random monotone scenarios

For random-scenario simulation studies, `PUA()` can be used to generate monotone dose-toxicity curves with a well-defined target dose.

```{r pua-example}
scen <- PUA(
  dose_set = 1:5,
  target_prob = 0.30,
  n_scenarios = 5
)

scen
```

## Development notes

`SKBD` is under active development. The current version focuses on core simulation engines and decision-table utilities for the SKBD framework. Additional examples, validation materials, and extended tutorials can be added as the package evolves.
