---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# SKBD

`SKBD` implements the shared keyboard design (SKBD) for model-assisted phase I dose-finding trials. The package provides tools for

- constructing decision tables for the shared keyboard design,
- simulating operating characteristics under the standard SKBD,
- extending SKBD to time-to-event settings with late-onset toxicity, and
- evaluating adaptive dose insertion under a shared-keyboard framework.

The package is intended for method development, operating-characteristic evaluation, and practical exploration of shared keyboard decision rules in phase I oncology trials.

## Installation

`SKBD` is not currently on CRAN. You can install the development version from GitHub:

```{r install, eval = FALSE}
install.packages("remotes")
remotes::install_github("Jiangyan-Zhao/SKBD")
```

Then load the package:

```{r load}
library(SKBD)
```

## Main functions

The current public interface includes five main functions:

- `get_boundary_SKBD()` generates pre-tabulated decision boundaries for the shared keyboard design.
- `get_OC_SKBD()` simulates operating characteristics for the standard SKBD.
- `get_OC_TITE_SKBD()` simulates operating characteristics for the time-to-event shared keyboard design.
- `get_OC_Insert_SKBD()` simulates operating characteristics when adaptive dose insertion is allowed.
- `PUA()` generates random monotone dose-toxicity scenarios using a pseudo-uniform algorithm.

## Decision tables for SKBD

A typical starting point is to generate a decision table at a current dose level, conditional on the observed data across doses.

```{r boundary-example}
y <- c(0, 1, 2, 2, 0)
n <- c(3, 6, 9, 3, 0)

out_boundary <- get_boundary_SKBD(
  target_prob = 0.30,
  d = 3,
  y = y,
  n = n,
  table_type = "continue"
)

out_boundary$boundary_tab
```

This returns a keyboard-style table with escalation, de-escalation, and elimination boundaries based on the SKBD pseudo-posterior at the current dose.

## Simulating operating characteristics under SKBD

The standard SKBD can be evaluated under a prespecified toxicity scenario as follows:

```{r oc-skbd}
out_skbd <- get_OC_SKBD(
  target_prob = 0.30,
  tox_prob = c(0.05, 0.12, 0.30, 0.45, 0.60),
  n_cohort = 10,
  cohort_size = 3,
  n_trial = 1000
)

out_skbd$PCS
out_skbd$PCA
out_skbd$ROD60
```

The returned object includes accuracy and safety summaries such as percent correct selection (`PCS`), percent correct allocation (`PCA`), and overdosing risk.

## Time-to-event SKBD

Late-onset toxicity can be handled through the time-to-event shared keyboard design:

```{r oc-tite}
out_tite <- get_OC_TITE_SKBD(
  target_prob = 0.20,
  tox_prob = c(0.05, 0.12, 0.20, 0.35, 0.50),
  n_cohort = 10,
  cohort_size = 3,
  tau = 3,
  accrual = 2,
  dist_DLT = "weibull",
  dist_enter = "exp",
  n_trial = 1000
)

out_tite$PCS
out_tite$duration_mean
```

This version accounts for pending toxicity outcomes through weighted follow-up within the DLT assessment window.

## Adaptive dose insertion

The package also supports simulations under an insertion-enabled shared keyboard design:

```{r oc-insert, eval = FALSE}
out_insert <- get_OC_Insert_SKBD(
  target_prob = 0.30,
  tox_prob = c(0.14, 0.45, 0.63, 0.74, 0.80),
  dose_set = c(5, 15, 25, 35, 45),
  n_trial = 1000
)

out_insert$insertion
```

The insertion summary reports how often new doses are inserted, where inserted doses tend to be selected, and how patients are allocated to inserted doses.

## Random monotone scenarios

For random-scenario simulation studies, `PUA()` can be used to generate monotone dose-toxicity curves with a well-defined target dose.

```{r pua-example}
scen <- PUA(
  dose_set = 1:5,
  target_prob = 0.30,
  n_scenarios = 5
)

scen
```

## Development notes

`SKBD` is under active development. The package currently focuses on core simulation and decision-table tools for the shared keyboard framework. Additional examples, validation materials, and extended documentation can be added as the package evolves.
